Ground state energy of quantum dots using the coupled cluster method

### 2018-05-24 project_2/article/article.tex

		Now comes the rather tedious task of evaluating all the terms 
		that arises from inserting \autoref{eq:normal_order_expansion}
		into \autoref{eq:doubles_amplitude_1}. This can be done by applying
		Wick's generalised theorem, but the task is a daunting and streneous one.
		A few example computations of how this can be done is included in
		\autoref{app:wickOnAmplitude}.
	 	Instead of doing it in this manner, we employ the second quantisation library
	 	from SymPy instead\footnote{This is also more in the spirit of this project,
	 	as it is within the realm of \emph{Computational} Physics.}.
		The CCD amplitude equation, from SymPy computation, is 
		\begin{equation}
		\begin{aligned}
			0 =& u^{ab}_{ij} + t^{ac}_{ij} u^{bm}_{cm} P(ab) + t^{ab}_{ik} u^{mk}_{jsm} P(ij) \\
				 +& \frac{1}{4}t^{cd}_{ij} t^{ab}_{nm} u^{nm}_{cd} + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd} \\
				 -& \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{nm}_{cd} P(ij) - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab) \\
				 -& t^{ac}_{im} t^{bd}_{jn} u^{nm}_{cd} P(ij) + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
				 +& \frac{1}{2}t^{ab}_{nm} u^{nm}_{ij}. 
		\end{aligned}
		\end{equation}

@@

				 =& f_{bc}t^{ac}_{ij}P(ab) - f_{kj}t^{ab}_{ik} \\
				 =& (h^c_b + u_{cm}^{bm})t_{ij}^{ac}P(ab) + (h^j_m + u_{jm}^{mk})t_{ik}^{ab}P(ij)

@@

		Where in the last steps we have consigned the sums by Einstein summation notation,
		and split the Fock operator into one- and two-body parts.

>>>>

		Now comes the rather tedious task of evaluating all the terms 
		that arises from inserting \autoref{eq:normal_order_expansion}
		into \autoref{eq:doubles_amplitude_1}. This can be done by applying
		Wick's generalised theorem, but the task is a daunting and streneous one.
		A few example computations of how this can be done is included in
		\autoref{app:wickOnAmplitude}.
	 	Instead of doing it in this manner, we employ the second quantisation library
	 	from SymPy instead\footnote{This is also more in the spirit of this project,
	 	as it is within the realm of \emph{Computational} Physics.}.
		The CCD amplitude equation, from SymPy computation, is 
		\begin{equation}
		\begin{aligned}
			0 =& u^{ab}_{ij} + f_{bc}t^{ac}_{ij}P(ab) - f_{kj}t^{ab}_{ik}P(ij) \\
				 +& \frac{1}{4}t^{cd}_{ij} t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd} \\
				 +& \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{mn}_{cd} P(ij) - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab) \\
				 +& t^{ac}_{im} t^{bd}_{jn} u^{mn}_{cd} P(ij) + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
				 +& \frac{1}{2}t^{ab}_{mn} u^{mn}_{ij}. 
		\label{eq:CCD_amp_1}
		\end{aligned}
		\end{equation}

		\subsubsection{The Iterative Scheme}
		Now we pick only diagonal elements of $f$ to be part of the unperturbed 
		Hamiltonian and let the other parts be for a while as part of a perturbation. 
		The second and third terms in \autoref{eq:CCD_amp_1} can now be 
		rewritten,
		\begin{equation}
		\begin{aligned}
			f_{bc}&t_{ij}^{ab}P(ab) - f_{kj}t_{ik}^{ab}P(ab) \\
				&= f_{bb}t_{ij}^{ab} - f_{aa}t_{ij}^{ba} - f_{jj}t_{ij}^{ab} + f_{ii}t_{ji}^{ab} \\
				&= (f_{aa} + f_{bb} - f_{ii} - f_{jj})t_{ij}^{ab} \\
				&= (\epsilon_a + \epsilon_b - \epsilon_i - \epsilon_j)t_{ij}^{ab} \\
				&= -(\epsilon_i + \epsilon_j - \epsilon_a - \epsilon_b)t_{ij}^{ab} \\				
				&= -D_{ij}^{ab}t_{ij}^{ab}.
		\end{aligned}
		\end{equation}

		Now, we define a new function consisting of all of \autoref{eq:CCD_amp_1} 
		except term number two and three,
		\begin{equation}
		\begin{aligned}		
			g(u, \tau) =&
				    \frac{1}{4}t^{cd}_{ij} t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd} \\
				 & \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{mn}_{cd} P(ij) - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab) \\
				 +& t^{ac}_{im} t^{bd}_{jn} u^{mn}_{cd} P(ij) + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
				 +& \frac{1}{2}t^{ab}_{mn} u^{mn}_{ij}, 
		\end{aligned}
		\end{equation}

		so that $D_{ij}^{ab}t_{ij}^{ab} = g(u, \tau)$. This allows us to define an iterative scheme,
		\begin{equation}
			\tau^{(k + 1)} = \frac{g(u, \tau^{(k)})}{D_{ij}^{ab}},
		\end{equation}
		with the initial guess
		\begin{equation}
			\tau^{(0)} = \frac{u_{ij}^{ab}}{D_{ij}^{ab}}.
		\end{equation}

@@

				 =& f_{bc}t^{ac}_{ij}P(ab) - f_{kj}t^{ab}_{ik}P(ij)

@@

		Where in the last steps we have consigned the sums by Einstein summation notation.
